---
title: "Portfolio 1 - Distractor Suppression Pilot Study"
name: "Cat Seitz"
date: "1.21.2023"
data: "Distractor Suppression Pilot Study"
output: 
  html_document: 
    theme: cerulean
---


```{r load-packages, message=FALSE}
library(tidyverse) 
library(tidyr)
library(rstatix)
library(data.table)
library(afex)
library(emmeans)
library(psych)
library(ggprism)
library(patchwork)
library(magrittr)
library(cowplot)
```

The data used is from a visual search task in which participants are searching for a unique item in an array of six items and press a button to indicate whether the item is facing right or left. On 50% of trials, a salient, color distractor is present in the array. On 67% of distractor present trials, the distractor appears in the same location in the array with an equal number of trials in the other 5 locations. This study is testing whether adults can learn to suppress their attention to the high-probabilty location of the distractor. 

The goal of this portfolio piece was to examine the distractor location effect on response times with regard to the statistical regularity introduced. 

```{r import data}

pilot <- read_csv("p01/p01/data/pilot_final.csv", show_col_types = FALSE)
  
```

Changed the value of column relative_hp_dist and changed RT column to milliseconds. Tried mutate and transform functions to no avail. 

```{r add new column for distractor location}
pilot$relative_hp_dist[pilot$relative_hp_dist == 10] <- "no_dist"
pilot$relative_hp_dist[pilot$relative_hp_dist == 0] <- "dist_0"
pilot$relative_hp_dist[pilot$relative_hp_dist == 1] <- "dist_1"
pilot$relative_hp_dist[pilot$relative_hp_dist == 2] <- "dist_2"
pilot$relative_hp_dist[pilot$relative_hp_dist == 3] <- "dist_3"

pilot$RT <- pilot$RT *1000
```

Add the block number to each trial because later I'll examine the block by block differences. 

```{r add block number}
block_num <- rep(c(1,2,3,4,5,6,7,8), each=60, times=21)
pilot <- cbind(pilot, block_num)

```

### Trim the Data

Define trimming criteria according to Van Selst and Jolicoeur 1994.
```{r set_stds_depending_on_set_size}
xsize <- c(4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 20, 
             25, 30, 35, 50, 100)
stds <- c(1.458, 1.68, 1.841, 1.961, 2.05, 2.12, 2.173, 
            2.22, 2.246, 2.274, 2.31, 2.326, 2.391, 2.41, 2.4305, 
            2.45, 2.48, 2.5)
```

Trim the data and compute the percent trimmed
```{r trimming}
trimmed <- pilot[pilot$acc==100, ] %>% group_by(ID, relative_hp_dist) %>%
           mutate(sdc = ifelse(length(RT)>=100,2.5,approx(xsize,stds,xout=length(RT))$y), avg = mean(RT), stdev = sd(RT)) %>%
           filter(RT <= sdc*stdev+avg & RT >=avg-(sdc*stdev) & RT >=.200) %>%
           select(ID, relative_hp_dist, RT, block_num) %>%  #keep these columns in the new data frame
           as.data.frame()


statPrep <- trimmed %>% group_by(ID, relative_hp_dist) %>% summarise(measurement=mean(RT)) %>% as.data.frame()
100-(nrow(trimmed)/nrow(pilot[pilot$acc==100, ]))*100
```
2.51% of trials were trimmed. 

### Distractor Location Effects on Response Times


Create new data frame with the mean response times grouped by distractor location relative to the high-probability location and add columns for standard error. Use this data frame for figure 1. 

```{r create new df with mean rts}

sum_stats <- trimmed%>%
  group_by(relative_hp_dist)%>%
  summarize(mean_rts=mean(RT),
            sd_rt=sd(RT),
            n_rt=21,
            se=sd_rt/sqrt(n_rt),
            upper_limit=mean_rts+se,
            lower_limit=mean_rts-se
  )
sum_stats

```



This figure displays the mean response times depending on the location of the distractor relative to the high probability location. I chose those particular colors based on Wake Forest's color scheme. 


```{r - graph 1 - distractor location effect on rt}
a<-ggplot(data = sum_stats, aes(x = relative_hp_dist, y = mean_rts)) +
  #geom_point()+
  geom_bar(stat = "identity", fill="blue", color='#000000') + ##9E7E38
  geom_errorbar(aes(ymin=lower_limit, ymax=upper_limit), width=0.2)+
  coord_cartesian(ylim = c(700,1050))+
  theme_classic()+
  labs(x = "Distractor Location", y = "Response Time (ms)")+
  labs(title = "Singleton Distractor Present")+
  #labs(caption = "An ANOVA test shows a difference in RT depending on distractor location, F(3.28,65.57)=33.3, p<.001.")+
  theme(axis.text=element_text(size=30),
        axis.title=element_text(size=40,face="bold"),
        title = element_text(size = 40))+
  scale_x_discrete(labels= c("no_dist"="no-dist","dist_0"="dist-0","dist_1"="dist-1","dist_2"="dist-2","dist_3"="dist-3"))
  
```



Create a new data frame with the average RT for each relative distractor location per participant, so we can do a repeated measures ANOVA. 

```{r smaller df for 1 line per condition per participant}

space <- trimmed %>%
  group_by(ID, relative_hp_dist) %>%
  summarize(rts = mean(RT)
            )
space
  
```

Create new data frame for only the first half of trials to test whether the differences between groups is significant when we cut the trials down. We want to do this because we are running this experiment with children ages 6-12 and want to make the experiment as short as possible. 

```{r cut out blocks 5-8}

df2 <- subset(trimmed,block_num!='7' )
df2 <- subset(df2,block_num!='8')
df2 <- subset(df2,block_num!='5' )
df2 <- subset(df2,block_num!='6')

space2<- df2 %>%
  group_by(ID, relative_hp_dist) %>%
  summarize(rts = mean(RT)
            )
space2

```

Test whether there is a difference between conditions for the first 4 blocks using a repeated measures ANOVA -- it is significant F(2.7,54)=25.06, p<.001. 

```{r subset_anova_test}

aov_car(rts ~ relative_hp_dist + Error(ID/relative_hp_dist), data=space2)

```

Need to reformat the above df to have a column for each relative_hp_dist/ID so we can run tests on the assumptions of ANOVAs. 

```{r}

space_anova <- setDT(space)
space_anova <- dcast(space_anova,ID~relative_hp_dist,value.var='rts')

```

``` {r testing assumptions}

#first identify outliers - not sure what to do with them anyway so overall just ignore? maybe reason enough to get rid of ppt 11?
space %>%
  group_by(relative_hp_dist) %>%
  identify_outliers(rts)


#testing the normality assumption -- data is not normally distributed because some conditions have a p-value less than .05
space %>%
  group_by(relative_hp_dist) %>%
  shapiro_test(rts)

```

Assumption of sphericity is automatically checked during the ANOVA test. Next, we using 3 different ways to run an ANOVA test -- . The ANOVA shows a significant difference among distractor locations, F(3.28,65.57)=33.3, p<.001. The 3 different methods used to run the ANOVA all gave significant results, but we'll go with the last test because it best takes into account the type of data we are using. 


```{r ANOVA test}

res.aov <- anova_test(data = space, dv = rts, wid = ID, within = relative_hp_dist)
get_anova_table(res.aov)

```

```{r anova_distractor_rts}

model = aov(rts~factor(relative_hp_dist)+
                Error(factor(ID)), data=space)
summary(model)

```

```{r last_anova_test}

model2 <- aov_car(rts ~ relative_hp_dist + Error(ID/relative_hp_dist), data=space)

model2


```

Test whether the high-prob location and the average across low-prob locations were significantly different. Using a paired samples t-test, I found that the response times for when the distractor was presented in the high-probability location compared to the average response time across the low-probability locations was significantly different (t(20)=4.95, p<.001). I also examined whether there were significant differences between the high-prob and distractor absent conditions and the low-prob and distractor absent conditions, using paired samples t-tests. All were significantly different with a p of <.001. 

```{r set up data for t-test for high and low conditions only}

space_anova <- space_anova %>%
  mutate(low_prob = (dist_1+dist_2+dist_3)/3)

```

```{r t-test}

space_anova %>%
  t.test(x=space_anova$low_prob, y=space_anova$dist_0, alternative="greater", mu=0,paired = TRUE, conf.level = .95) 
space_anova%>%
  t.test(x=space_anova$dist_0, y=space_anova$no_dist, alternative="greater", mu=0, paired =TRUE, conf.level = .95) 
space_anova%>%
  t.test(x=space_anova$low_prob, y=space_anova$no_dist, alternative="greater", mu=0, paired =TRUE, conf.level = .95)

```

Now, I want to create a smaller graph with just 3 bars: one for the high-probability rts, average of low-probability rts, and no distractor. 

```{r get_info_for_smaller_figure}

df_mod <- subset(space_anova, select=c(ID, no_dist, dist_0, low_prob))

df_mod <- reshape2::melt(df_mod, id.var=c('ID'), variable.name= "relative_hp_dist")

```

```{r another_df_with_mean_rts}

sum_stats2 <- df_mod%>%
  group_by(relative_hp_dist)%>%
  summarize(mean_rts=mean(value),
            sd_rt=sd(value),
            n_rt=21,
            se=sd_rt/sqrt(n_rt),
            upper_limit=mean_rts+se,
            lower_limit=mean_rts-se
  )
sum_stats2

```

In order to add the p-values to the graph, I needed to create data frames fo reach value and specify the position on the graph; then, use add_pvalue with ggplot. 

```{r adding-p-values}

result<- .001


#Make df for adding the p-value 
p_val1<- data.frame(
  group_1="dist_0",
  group_2="low_prob",
  label=result,
  y.position=1050
)

p_val2<- data.frame(
  group_1="no_dist",
  group_2="low_prob",
  label=result,
  y.position=1150
)

p_val3<- data.frame(
  group_1="no_dist",
  group_2="dist_0",
  label=result,
  y.position=950
)


```

This figure displays the mean response times depending on the location of the distractor relative to the high probability location. I chose those particular colors based on Wake Forest's color scheme. 


```{r - graph 2 - distractor location effect on rt}
ggplot(data = sum_stats2, aes(x = relative_hp_dist, y = mean_rts)) +
  geom_bar(stat = "identity", fill="#9E7E38", color='#000000') +
  geom_errorbar(aes(ymin=lower_limit, ymax=upper_limit), width=0.2)+
  coord_cartesian(ylim = c(700,1200))+
  theme_classic()+
  add_pvalue(p_val1,
             xmin = "group_1",
             xmax = "group_2",
             label = "p < {label}",
             y.position = "y.position",
             label.size = 4,
             bracket.size = .5)+
  add_pvalue(p_val2,
             xmin = "group_1",
             xmax = "group_2",
             label = "p < {label}",
             y.position = "y.position",
             label.size = 4,
             bracket.size = .5)+
  add_pvalue(p_val3,
             xmin = "group_1",
             xmax = "group_2",
             label = "p < {label}",
             y.position = "y.position",
             label.size = 4,
             bracket.size = .5)+
  labs(x = "Distractor Location", y = "Response Time (ms)")+
  labs(title = "Distractor Location Effect on RT")+
  #labs(caption = "An ANOVA test shows a difference in RT depending on distractor location, F(1.97,39.33)=67.98, p<.001.")+
    theme(axis.text=element_text(size=12),
        axis.title=element_text(size=18,face="bold"),
        title = element_text(size = 20))+
  scale_x_discrete(labels= c("no_dist"="Distractor Absent","low_prob"="Low Prob Location", "dist_0"="High Prob Location"))
  
```

One last ANOVA test on this subset of data. 

```{r 3_loc_anova_test}

model3 <- aov_car(value ~ relative_hp_dist + Error(ID/relative_hp_dist), data=df_mod)

model3


```

Combine graphs of rt and accuracy for NC Cog Poster.

```{r create_accuracy_df}

pilot_distacc <- pilot %>%
  group_by(relative_hp_dist) %>%
  summarize(accuracy = mean(acc),
            sd_rt=sd(acc),
            n_rt=21,
            se=sd_rt/sqrt(n_rt),
            upper_limit=accuracy+se,
            lower_limit=accuracy-se
            )

b<-ggplot(data = pilot_distacc, aes(x = relative_hp_dist, y = accuracy)) +
  geom_bar(stat = "identity", fill="#9E7E38", color='#000000') +
  geom_errorbar(aes(ymin=lower_limit, ymax=upper_limit), width=0.2)+
  coord_cartesian(ylim = c(85,105))+
  theme_classic()+
  labs(x = "Distractor Location", y = "Accuracy (%)")+
  #labs(title = "Distractor Location Effect on Accuracy")+
  theme(axis.text=element_text(size=30),
        axis.title=element_text(size=40,face="bold"),
        title = element_text(size = 24))+
  scale_x_discrete(labels= c("no_dist"="no-dist","dist_0"="dist-0","dist_1"="1","dist_2"="2","dist_3"="3"))


```

```{r dist_2-plots, fig.height=11, fig.width=22} 
#
plot_grid(a,b,labels = c('A','B'), label_size=20, rel_widths = c(2,1))
  

```

### Examine block-by-block learning of distractor location

The goal of this section is to examine individual blocks of trials for learning. I'll be taking the difference between response times when the distractor is presented in the low probability locations and response times when the distractor is presented in the high probability location in each block to see roughly how quickly individuals are learning the regularity.


```{r create_new_df_to_transform}
space_block <- trimmed %>%
  group_by(ID, block_num, relative_hp_dist) %>%
  summarize(rts = mean(RT),
            )
space_block
```

```{r transform_df}

space_block <- setDT(space_block)
space_block <- dcast(space_block,ID+block_num~relative_hp_dist,value.var='rts')

```

Below, I added the average rt for the low probability locations and the difference between the low probability and high probability locations ignoring n/a values. 

```{r add_avg_col}

space_block <- space_block %>%
  mutate(low_prob = rowMeans(select(space_block, c(dist_1,dist_2,dist_3)),na.rm=TRUE)) %>%
  mutate(difference = (low_prob-dist_0))


```


```{r line_plot}
ggplot(data = space_block,aes(x=block_num, y=difference, group=ID))+
  geom_line(aes(color=ID))+
  geom_point()+
  labs(title = "Difference in Response Times", subtitle = "for distractor presentation at the low-probability locations and high-probability location by block")+
  theme_classic()+
  labs(x = "Block Number", y = "Difference in RT (ms)")

```


Positive differences indicate that participants were faster when the distractor was presented in the high probability location compared to when it was presented in the low probability locations. The average across all participants is plotted below. These results indicate that the individuals are learning within the first block where the distractor is likely to appear. 



```{r create_df_to_transform}
space2 <- space_block %>%
  group_by(block_num) %>%
  summarize(rts = mean(difference, na.rm = TRUE),
            sd_rt=sd(difference, na.rm = TRUE),
            n_rt=21,
            se=sd_rt/sqrt(n_rt),
            upper_limit=rts+se,
            lower_limit=rts-se
            )

```

```{r line_plot_avg, fig.height=4, fig.width=12}
ggplot(data = space2,aes(x=block_num, y=rts))+
  geom_line()+
  geom_point()+
  geom_errorbar(aes(ymin=lower_limit, ymax=upper_limit), width=0.2)+
  labs(title = "Singleton Distractor Present")+
  xlab("Block number")+
  ylab(expression(atop("Suppression effect (ms)", paste("(high prob. - low prob.)"))))+
  theme(axis.text=element_text(size=14),
        axis.title=element_text(size=14,face="bold"),
        title = element_text(size = 16))

```


```{r anova_test_by_block}

model4 <- aov_car(difference ~ block_num + Error(ID/block_num), data=space_block)

summary(model4)
model4

```

### CDT correlation with suppression effect

```{r cdt-load}

cdt <- read_csv("RawData_pilot_CDT.csv", show_col_types = FALSE)

```


```{r add-cases}
cdt <- cdt %>%
  mutate(outcome=
           case_when(Accurate==1 & Change==1 ~ "hit",
                     Accurate==1 & Change==0 ~ "cor_rej",
                     Accurate==0 & Change==1 ~ "miss",
                     Accurate==0 & Change==0 ~ "f_alarm",
           ))

```

```{r count-cases}

cdt<-cdt%>%
  group_by(SubID, SetSize)%>%
  count(outcome)

```

Reformat to have column for each outcome

```{r reformat-cdt}

cdt1 <- setDT(cdt)
cdt1 <- dcast(cdt1,SubID+SetSize~outcome,value.var='n')

```

```{r NA-to-zero}

cdt1[is.na(cdt1)] <- 0


```


```{r calc-hit-rate}

cdt1<-cdt1 %>%
  mutate(hit_rate = hit/(hit+miss))

```

```{r calc-false-alarm-rate}

cdt1<-cdt1 %>%
  mutate(fa_rate = f_alarm/(f_alarm+cor_rej))

```

```{r calc-capacity}

cdt1<-cdt1 %>%
  mutate(K = SetSize*(hit_rate-fa_rate))

```

Need to make a new data frame with the average capacity per participant. 

```{r avg-K}

capacity <- cdt1 %>%
  group_by(SubID) %>%
  summarize(avg_k = mean(K))

```

```{r suppression-effect}

supp <- space_block %>%
  group_by(ID)%>%
  summarize(effect = mean(difference, na.rm = TRUE))

supp

```

```{r merge}

df <- cbind(capacity, supp)

df <- df %>% 
  select(-c("ID"))

```

```{r correlation}

cor.test(df$effect, df$avg_k)

```

