---
title: "Portfolio 1"
name: "Cat Seitz"
date: "1.21.2023"
data: "Distractor Suppression Pilot Study"
---

> The projects should be numbered consecutively (i.e., in the order in which you began them), and should include for each project a description of the goal, the product (computer program, hand graph, computer graph, etc.), the data, and some interpretation. Reports must be reproducible and of high quality in terms of writing, grammar, presentation, etc.

```{r load-packages, message=FALSE}
library(tidyverse) 
library(tidyr)
library(rstatix)
```

The data used is from a visual search task in which participants are searching for a unique item in an array of six items and press a button to indicate whether the item is facing right or left. On 50% of trials, a salient, color distractor is present in the array. On 67% of distractor present trials, the distractor appears in the same location in the array with an equal number of trials in the other 5 locations. This study is testing whether adults can learn to suppress their attention to the high-probabilty location of the distractor. 

```{r import data}

pilot <- read_csv("p01/data/pilot_final.csv", show_col_types = FALSE)
  
```
Question: is there an easier/simpler way to change the column? -- rename; as factor?

Changed the value of column relative_hp_dist. Tried mutate and transform functions to no avail. 

```{r add new column for distractor location}
pilot$relative_hp_dist[pilot$relative_hp_dist == 10] <- "no dist"
pilot$relative_hp_dist[pilot$relative_hp_dist == 0] <- "0 dist"
pilot$relative_hp_dist[pilot$relative_hp_dist == 1] <- "1 dist"
pilot$relative_hp_dist[pilot$relative_hp_dist == 2] <- "2 dist"
pilot$relative_hp_dist[pilot$relative_hp_dist == 3] <- "3 dist"

pilot$RT <- pilot$RT *1000
```

Create new data frame with the mean response times grouped by distractor location relative to the high-probability location and change RT column to milliseconds. 

```{r create new df with mean rts}

dist_means <- pilot %>%
  group_by(relative_hp_dist) %>%
  filter(acc==100) %>%
  summarize(mean_rts=mean(RT),
            sd_rt=sd(RT),
            n_rt=21,
            se=sd_rt/sqrt(n_rt),
            upper_limit=mean_rts+se,
            lower_limit=mean_rts-se
  )
dist_means

```

This figure displays the mean response times depending on the location of the distractor relative to the high probability location. Choose those particular colors based on Wake Forest's color scheme. 


```{r - graph 1 - distractor location effect on rt}
ggplot(data = dist_means, aes(x = relative_hp_dist, y = mean_rts)) +
  geom_bar(stat = "identity", fill="#9E7E38", color='#000000') +
  geom_errorbar(aes(ymin=lower_limit, ymax=upper_limit), width=0.2)+
  coord_cartesian(ylim = c(700,1050))+
  theme_classic()+
  labs(x = "Distractor Location", y = "Response Time (ms)")+
  labs(title = "Distractor Location Effect on RT")
  
```
Create a new data frame with the average RT for each relative distractor location per participant, so we can do a repeated measures ANOVA. 

```{r smaller df for 1 line per condition per participant}

space <- pilot %>%
  group_by(ID, relative_hp_dist) %>%
  filter(acc==100) %>%
  summarize(rts = mean(RT),
            )
space
  
```

