---
title: "Portfolio 2"
name: "Cat Seitz"
date: "1.31.2023"
data: "Distractor Suppression Pilot Study"
---

```{r load-packages, message=FALSE}
library(tidyverse) 
library(tidyr)
library(rstatix)
library(data.table)
library(afex)
library(emmeans)
library(psych)
library(ggsignif)
library(ggprism)
library(patchwork)
library(magrittr)
library(cowplot)
```

The data used is from a visual search task in which participants are searching for a unique item in an array of six items and press a button to indicate whether the item is facing right or left. On 50% of trials, a salient, color distractor is present in the array. On 67% of distractor present trials, the distractor appears in the same location in the array with an equal number of trials in the other 5 locations. This study is testing whether adults can learn to suppress their attention to the high-probabilty location of the distractor. 

The goal of this portfolio is to examine the effects of distractor location on accuracy and target location on response time and accuracy. 

```{r import_data}

pilot <- read_csv("p02/pilot_final.csv", show_col_types = FALSE)

pilot$relative_hp_dist[pilot$relative_hp_dist == 10] <- "no_dist"
pilot$relative_hp_dist[pilot$relative_hp_dist == 0] <- "dist_0"
pilot$relative_hp_dist[pilot$relative_hp_dist == 1] <- "dist_1"
pilot$relative_hp_dist[pilot$relative_hp_dist == 2] <- "dist_2"
pilot$relative_hp_dist[pilot$relative_hp_dist == 3] <- "dist_3"
pilot$RT <- pilot$RT *1000
  
```

### Target Location Effects on Response Time

Added in the block column at this point just in case I want to use it in the future. 

```{r add_column_for_trial_block}

block_num <- rep(c(1,2,3,4,5,6,7,8), each=60, times=21)
pilot <- cbind(pilot, block_num)

```

Added in a column for how the target related to the high-probability distractor location. Used brute force instead of trying to write a fancy function. 

```{r add_column_for_target_distance_from_the_high_probability_location}

pilot <- pilot %>%
  mutate(relative_target=
           case_when(target_loc=="loc1" & high_prob==1 ~ 0,
                     target_loc=="loc2" & high_prob==1 ~ 1,
                     target_loc=="loc3" & high_prob==1 ~ 2,
                     target_loc=="loc4" & high_prob==1 ~ 3,
                     target_loc=="loc5" & high_prob==1 ~ 2,
                     target_loc=="loc6" & high_prob==1 ~ 1,
                     target_loc=="loc1" & high_prob==2 ~ 1,
                     target_loc=="loc2" & high_prob==2 ~ 0,
                     target_loc=="loc3" & high_prob==2 ~ 1,
                     target_loc=="loc4" & high_prob==2 ~ 2,
                     target_loc=="loc5" & high_prob==2 ~ 3,
                     target_loc=="loc6" & high_prob==2 ~ 2,
                     target_loc=="loc1" & high_prob==3 ~ 2,
                     target_loc=="loc2" & high_prob==3 ~ 1,
                     target_loc=="loc3" & high_prob==3 ~ 0,
                     target_loc=="loc4" & high_prob==3 ~ 1,
                     target_loc=="loc5" & high_prob==3 ~ 2,
                     target_loc=="loc6" & high_prob==3 ~ 3,
                     target_loc=="loc1" & high_prob==4 ~ 3,
                     target_loc=="loc2" & high_prob==4 ~ 2,
                     target_loc=="loc3" & high_prob==4 ~ 1,
                     target_loc=="loc4" & high_prob==4 ~ 0,
                     target_loc=="loc5" & high_prob==4 ~ 1,
                     target_loc=="loc6" & high_prob==4 ~ 2,
                     target_loc=="loc1" & high_prob==5 ~ 2,
                     target_loc=="loc2" & high_prob==5 ~ 3,
                     target_loc=="loc3" & high_prob==5 ~ 2,
                     target_loc=="loc4" & high_prob==5 ~ 1,
                     target_loc=="loc5" & high_prob==5 ~ 0,
                     target_loc=="loc6" & high_prob==5 ~ 1,
                     target_loc=="loc1" & high_prob==6 ~ 1,
                     target_loc=="loc2" & high_prob==6 ~ 2,
                     target_loc=="loc3" & high_prob==6 ~ 3,
                     target_loc=="loc4" & high_prob==6 ~ 2,
                     target_loc=="loc5" & high_prob==6 ~ 1,
                     target_loc=="loc6" & high_prob==6 ~ 0,))

pilot$relative_target[pilot$relative_target == 0] <- "high_prob"
pilot$relative_target[pilot$relative_target == 1] <- "lp_1"
pilot$relative_target[pilot$relative_target == 2] <- "lp_2"
pilot$relative_target[pilot$relative_target == 3] <- "lp_3"

```

### Trim the Data

Define trimming criteria according to Van Selst and Jolicoeur 1994
```{r set_stds_depending_on_set_size}
xsize <- c(4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 20, 
             25, 30, 35, 50, 100)
stds <- c(1.458, 1.68, 1.841, 1.961, 2.05, 2.12, 2.173, 
            2.22, 2.246, 2.274, 2.31, 2.326, 2.391, 2.41, 2.4305, 
            2.45, 2.48, 2.5)
```

Trim the data and compute the percent trimmed
```{r trimming}
add_this<- pilot[pilot$acc==100,]

trimmed <- add_this[add_this$relative_hp_dist=="no_dist",] %>% 
  group_by(ID, relative_target) %>%
           mutate(sdc = ifelse(length(RT)>=100,2.5,approx(xsize,stds,xout=length(RT))$y), avg = mean(RT), stdev = sd(RT)) %>%
           filter(RT <= sdc*stdev+avg & RT >=avg-(sdc*stdev) & RT >=.200) %>%
           select(ID, relative_hp_dist, RT, block_num, relative_target) %>%
           as.data.frame()


statPrep <- trimmed %>% group_by(ID, relative_target) %>% summarise(measurement=mean(RT)) %>% as.data.frame()
100-(nrow(trimmed)/nrow(add_this[add_this$relative_hp_dist=="no_dist",]))*100
```
Again, trimmed 2.69% of trials. 

###Target Location Effects

Create new data frame with the mean response times grouped by distractor location relative to the high-probability location and add columns for standard error. 

```{r create new df with mean rts}

target_means <- trimmed %>%
  filter(relative_hp_dist=="no_dist") %>%
  group_by(relative_target) %>%
  summarize(mean_rts=mean(RT),
            sd_rt=sd(RT),
            n_rt=21,
            se=sd_rt/sqrt(n_rt),
            upper_limit=mean_rts+se,
            lower_limit=mean_rts-se
  )
target_means

```

This figure displays the mean response times depending on the location of the target relative to the high probability location of the distractor. I chose those particular colors based on Wake Forest's color scheme. 


```{r - graph 1 - distractor location effect on rt, fig.height=9, fig.width=12}
c<-ggplot(data = target_means, aes(x = relative_target, y = mean_rts, fill=relative_target)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  geom_errorbar(aes(ymin=lower_limit, ymax=upper_limit), width=0.2)+
  coord_cartesian(ylim = c(700,1000))+
  theme_classic()+
  scale_fill_brewer(palette="Dark2")+
  labs(x = "Target Location", y = "Response Time (ms)")+
  labs(title = "Singleton Distractor Absent")+
  theme(axis.text=element_text(size=30),
    axis.title=element_text(size=40,face="bold"),
    title = element_text(size = 40))+
  scale_x_discrete(labels= c("high_prob"="HP loc","lp_1"="dist-1", "lp_2"="dist-2", "lp_3"="dist-3"))
  
```


```{r cut out blocks 7 and 8}

df2 <- subset(trimmed,block_num!='7' & relative_hp_dist=="no_dist")
df2 <- subset(df2,block_num!='8')
df2 <- subset(df2,block_num!='5')
df2 <- subset(df2,block_num!='6')

space2<- df2 %>%
  group_by(ID, relative_target) %>%
  summarize(rts = mean(RT)
            )
space2

```

```{r anove_trimmed_df}

aov_car(rts ~ relative_target + Error(ID/relative_target), data=space2)

```

Create a new data frame with the average RT for each relative distractor location per participant, so we can do a repeated measures ANOVA. 

```{r smaller df for 1 line per condition per participant}

space <- trimmed %>%
  subset(relative_hp_dist=="no_dist")%>%
  group_by(ID, relative_target) %>%
  summarize(rts = mean(RT),
            )
space
  
```

Need to reformat the above df to have a column for each relative_hp_dist/ID.

```{r}

space_anova <- setDT(space)
space_anova <- dcast(space_anova,ID~relative_target,value.var='rts')

```

``` {r testing assumptions}

#first identify outliers - not sure what to do with them anyway so overall just ignore? maybe reason enough to get rid of ppt 11? ppt 11 was problematic in most tests
space %>%
  group_by(relative_target) %>%
  identify_outliers(rts)


#testing the normality assumption -- data is normally distributed enough because no conditions have a p-value less than .05
space %>%
  group_by(relative_target) %>%
  shapiro_test(rts)

```

Assumption of sphericity is automatically checked during the ANOVA test. Next, we'll do the ANOVA test. The ANOVA shows a significant difference among distractor locations, F(1.74,34.86)=12.925, p<.001.


```{r ANOVA test}

res.aov <- anova_test(data = space, dv = rts, wid = ID, within = relative_target)
get_anova_table(res.aov)

```

I ran the ANOVA using base R as well because the rstatix package was giving me errors when running for accuracy data later on. The rstatix packages has a lot of requests and hasn't been updated in years so I switched to a different route to get the same results. 

```{r anova_target_rt}

model = aov(rts~factor(relative_target)+
                Error(factor(ID)), data=space)
summary(model)

```

```{r last_anova_test}

model2 <- aov_car(rts ~ relative_target + Error(ID/relative_target), data=space)

summary(model2)
model2


```

This next section will examine the differences between response times when averaging across low-probability locations. 

```{r get_low-prob_avg}

space_anova <- space_anova %>%
  mutate(low_prob = (lp_1+lp_2+lp_3)/3)

```

```{r get_info_for_smaller_figure}

df_mod <- subset(space_anova, select=c(ID, high_prob, low_prob))

df_mod <- reshape2::melt(df_mod, id.var=c('ID'), variable.name= "relative_target")

```

```{r another_df_with_mean_rts}

sum_stats2 <- df_mod%>%
  group_by(relative_target)%>%
  summarize(mean_rts=mean(value),
            sd_rt=sd(value),
            n_rt=n(),
            se=sd_rt/sqrt(n_rt),
            upper_limit=mean_rts+se,
            lower_limit=mean_rts-se
  )
sum_stats2

```

Determine if the difference between response times when the target is in the high-probability vs. low-probability locations is significant. 

```{r t-test}

t.test(x=space_anova$high_prob, y=space_anova$low_prob, alternative="greater", mu=0,paired = TRUE, conf.level = .95)

```


This figure displays the mean response times depending on the location of the target relative to the high probability location. I chose those particular colors based on Wake Forest's color scheme. 


```{r - graph 2 - target location effect on rt}

  
sum_stats2$relative_target <- factor(sum_stats2$relative_target,              # Change ordering manually
                  levels = c("high_prob", "low_prob"))

c<-ggplot(data = sum_stats2, aes(x = relative_target, y = mean_rts, fill=relative_target)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  geom_errorbar(aes(ymin=lower_limit, ymax=upper_limit), width=0.2)+
  coord_cartesian(ylim = c(700,1000))+
  theme_classic()+
  scale_fill_brewer(palette="Dark2") +
  labs(x = "Target Location", y = "Response Time (ms)")+
  labs(title = "Singleton Distractor Absent")+
  theme(axis.text=element_text(size=30),
        axis.title=element_text(size=40,face="bold"),
        title = element_text(size = 45))+
  scale_x_discrete(labels= c("high_prob"="HP loc","low_prob"="LP loc"))
  
```


Test for significant differences between the high and low prob locations for 6 blocks and 4 blocks. 

```{r t-test_half}

space_half <- setDT(space2)
space_half <- dcast(space_half,ID~relative_target,value.var='rts')

space_half <- space_half %>%
 mutate(low_prob = (lp_1+lp_2+lp_3)/3)

space_half %>%
  t.test(x=space_half$high_prob, y=space_half$low_prob, alternative="greater", mu=0,paired = TRUE, conf.level = .95)

```

Examine the summary statistics for subset of data.

```{r another_df_with_mean_rts_half}

df_mod2 <- subset(space_half, select=c(ID, high_prob, low_prob))
df_mod2 <- reshape2::melt(df_mod2, id.var=c('ID'), variable.name= "relative_target")

sum_stats3 <- df_mod2%>%
  group_by(relative_target)%>%
  summarize(mean_rts=mean(value),
            sd_rt=sd(value),
            n_rt=21,
            se=sd_rt/sqrt(n_rt),
            upper_limit=mean_rts+se,
            lower_limit=mean_rts-se
  )
sum_stats3

```

### Distractor and Target Location Effects on Accuracy


```{r create_accuracy_df}

pilot_distacc <- pilot %>%
  group_by(relative_hp_dist) %>%
  summarize(accuracy = mean(acc),
            sd_rt=sd(acc),
            n_rt=n(),
            se=sd_rt/sqrt(n_rt),
            upper_limit=accuracy+se,
            lower_limit=accuracy-se
            )

spaceT <- pilot %>%
  subset(relative_hp_dist=="no_dist")%>%
  group_by(ID, relative_target)%>%
  summarize(acc = mean(acc)
            )

space_anovaT <- setDT(spaceT)
space_anovaT <- dcast(space_anovaT,ID~relative_target,value.var='acc')

space_anovaT <- space_anovaT %>%
  mutate(low_prob = (lp_1+lp_2+lp_3)/3) 

df_mod_targ <- subset(space_anovaT, select=c(ID,high_prob, low_prob))
df_mod_targ <- reshape2::melt(df_mod_targ, id.var=c('ID'), variable.name= "relative_target")

pilot_targacc <- df_mod_targ %>%
  group_by(relative_target) %>%
  summarize(accuracy = mean(value),
            sd_rt=sd(value),
            n_rt=n(),
            se=sd_rt/sqrt(n_rt),
            upper_limit=accuracy+se,
            lower_limit=accuracy-se
            )



```


```{r - graph target location effects on accuracy, fig.height=9, fig.width=6}
d<-ggplot(data = pilot_targacc, aes(x = relative_target, y = accuracy, fill=relative_target)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  geom_errorbar(aes(ymin=lower_limit, ymax=upper_limit), width=0.2)+
  coord_cartesian(ylim = c(85,100))+
  theme_classic()+
  scale_fill_brewer(palette="Dark2")+
  labs(x = "Target Location", y = "Accuracy (%)")+
  theme(axis.text=element_text(size=30),
        axis.title=element_text(size=40,face="bold"),
        title = element_text(size = 45))+
  scale_x_discrete(labels= c("high_prob"="HP loc","low_prob"="LP loc"))
  
```

Created the below plot for NC Cognition Poster. 

```{r join-2-figures, fig.height=11, fig.width=22}

plot_grid(c,d,labels = c('C','D'), label_size=40, rel_widths = c(1.5,1))


```


```{r create_accuracy_df_for_ANOVAs}

pilot_dist <- pilot %>%
  group_by(ID, relative_hp_dist) %>%
  summarize(accuracy = mean(acc)
            )
pilot_dist
```

```{r accuracy_target}

pilot_targ <- pilot %>%
  subset(relative_hp_dist=="no_dist")%>%
  group_by(ID, relative_target) %>%
  summarize(accuracy = mean(acc)
            )

pilot_targ

```


```{r anova_distractor_accuracy}

model = aov(accuracy~factor(relative_hp_dist)+
                Error(factor(ID)), data=pilot_dist)
summary(model)

```
```{r last_anova_dist}

model2 <- aov_car(accuracy ~ relative_hp_dist + Error(ID/relative_hp_dist), data=pilot_dist)

model2


```

```{r anova_target_accuracy}

model = aov(accuracy~factor(relative_target)+
                Error(factor(ID)), data=pilot_targ)
summary(model)

```

```{r last_anova_target}

model2 <- aov_car(accuracy ~ relative_target + Error(ID/relative_target), data=pilot_targ)

model2


```

Create df and do t-test for HP and average of LP locations. 

```{r t-test-target-acc}

targ_t <- setDT(pilot_targ)
targ_t <- dcast(pilot_targ,ID~relative_target,value.var='accuracy')

targ_t <- targ_t %>%
  mutate(low_prob = (lp_1+lp_2+lp_3)/3)

targ_t %>%
  t.test(x=targ_t$low_prob, y=targ_t$high_prob, alternative="greater", mu=0,paired = TRUE, conf.level = .95) 


```

```{r t-test-distractor-acc}

dist_t <- setDT(pilot_dist)
dist_t <- dcast(pilot_dist,ID~relative_hp_dist,value.var='accuracy')

dist_t <- dist_t %>%
  mutate(low_prob = (dist_1+dist_2+dist_3)/3)

```

Running ANOVA on high-prob, low-prob, and distractor absent trials. 

```{r create-usable-df}

df_mod <- subset(dist_t, select=c(ID, no_dist, dist_0, low_prob))

df_mod <- reshape2::melt(df_mod, id.var=c('ID'), variable.name= "relative_hp_dist")

#run the ANOVA

anova_dist <- aov_car(value ~ relative_hp_dist + Error(ID/relative_hp_dist), data=df_mod)

anova_dist


```

```{r holm-correction}

df_mod %>%
  pairwise_t_test(
    value ~ relative_hp_dist, paired = TRUE,
    p.adjust.method = "holm"
    )


```

Examining only some of the block of trials. 

```{r half_data}
df3 <- subset(pilot,block_num!='7')
df3 <- subset(df3,block_num!='8')
df3 <- subset(df3,block_num!='5')
df3 <- subset(df3,block_num!='6')



```

```{r create_accuracy_df_for_ANOVAs_half}

pilot_dist3 <- df3 %>%
  group_by(ID, relative_hp_dist) %>%
  summarize(accuracy = mean(acc)
            )

```

```{r accuracy_target_half}

pilot_targ3 <- df3 %>%
  subset(relative_hp_dist="no_dist")%>%
  group_by(ID, relative_target) %>%
  summarize(accuracy = mean(acc)
            )


```

```{r anova_dist_half}

aov_car(accuracy ~ relative_hp_dist + Error(ID/relative_hp_dist), data=pilot_dist3)



```

```{r anova_target_half}

aov_car(accuracy ~ relative_target + Error(ID/relative_target), data=pilot_targ3)



```



