---
title: "Portfolio 4"
name: "Cat Seitz"
date: "02.28.2023"
data: ""
output: 
  html_document: 
    theme: cerulean
---


Goal: Examine the tidy tuesday dataset on chocolate bars
Product: Finding the best model for predicting chocolate bars ratings based on their cocoa percentage. 
Data: Chocolate Bar Ratings
Interpretation: A quadratic model fit the data best. This model shows that the highest rated chocolate bars did not have the highest or lowest cocoa percentage, but had a medium percentage of cocoa. 


```{r load-packages, message=FALSE}
library(tidyverse) 
library(tidyr)
library(tidytuesdayR)
library(tidymodels)
library(openintro)
library(broom)
```


```{r import-data}

tuesdata <- tidytuesdayR::tt_load('2022-01-18')
chocolate <- tuesdata$chocolate

```

First, convert the cocoa percentage column to numbers without the percent sign. Since this column is a string, we'll want to convert it to numeric. 

```{r change-percent}

chocolate$cocoa_percent<-gsub("%$","",chocolate$cocoa_percent)
chocolate<-transform(chocolate, cocoa_percent = as.numeric(cocoa_percent))
class(chocolate$cocoa_percent)

```

Based on my own experience, as the cocoa_percentage increases, the chocolate tastes worse -- too bitter. Let's see if this theory holds true with the raw data and in the taste of others. 


```{r plot-ratings-cocoa-percentage}


ggplot(chocolate, aes(y = rating, x=cocoa_percent))+
  geom_point()+
  stat_smooth(method="lm")+
  labs(title="Relationship between Cocoa Percentage and Rating", y="Rating", x="Cocoa Percentage")


```

```{r fit-linear-model-cocoa-percentage}

linear_reg() %>%
  set_engine("lm") %>%
  fit(rating ~ cocoa_percent, data = chocolate) %>%
  tidy()

```

```{r linear-model-summary}

summary(lm(rating ~ cocoa_percent, data=chocolate))

```

Using a linear model, the intercept isn't meaningful because no chocolate bar would have 0% of cocoa. Generally, if we increase cocoa percentage, rating of the chocolate decreases. The adjusted r-squared suggests that 2.1% of the variation in rating is accounted for by the cocoa percent. 


Taking a closer look at the scatterplot, it seems a quadratic regression model might fit the data better than a linear regression model. Let's explore that. 


```{r fit-quadratic-model}

#create percent squared variable
chocolate$cocoa_percent2<-chocolate$cocoa_percent^2

#fit quad regression model

quad_model <- lm(rating ~ cocoa_percent + cocoa_percent2, data=chocolate)

#view model

summary(quad_model)



```

This new model explains 6% of the total variance in chocolate bar ratings; and therefore, is a better model than the previous one. 


I'm attempting to plot the quadratic regression line but it isn't working using the code professor google told me to use, so I'm going to try something else. 

```{r plot-quad}

#create sequence of pct values
pctValues <- seq(40, 100, 0.1)

#create list of predicted happines levels using quadratic model
#rating_predict <- predict(quad_model,list(pcts=pctValues, pcts2=pctValues^2)) #

#create scatterplot of original data values
#plot(chocolate$cocoa_percent, chocolate$rating, pch=16)
#add predicted lines based on quadratic regression model
#lines(pctValues, rating_predict, col='blue')

```


Trying another method to plot the quadratic regression line. Looks like it worked!


```{r plot-quad-line}


ggplot(chocolate, aes(y = rating, x=cocoa_percent))+
  geom_jitter()+
  stat_smooth(method="lm",
              formula = y ~ poly(x, 2))+
  labs(title="Relationship between Cocoa Percentage and Rating", y="Rating", x="Cocoa Percentage")


```

I wanted to test this other way of fitting a quadratic model to make sure I got the same results as the method I used previously. 


```{r testing}
#fit quad regression model

quad_model2 <- lm(rating ~ poly(cocoa_percent, 2), data=chocolate)

#view model

summary(quad_model2)

```