---
title: "Portfolio 4"
name: "Cat Seitz"
date: "02.28.2023"
data: ""
output: 
  html_document: 
    theme: cerulean
---


Goal: 
Product: 
Data: Chocolate Bar Ratings
Interpretation: 


```{r load-packages, message=FALSE}
library(tidyverse) 
library(tidyr)
library(tidytuesdayR)
library(tidymodels)
library(openintro)
library(broom)
```


```{r import-data}

tuesdata <- tidytuesdayR::tt_load('2022-01-18')
chocolate <- tuesdata$chocolate

```

First, convert the cocoa percentage column to numbers without the percent sign. Since this column is a string, we'll want to convert it to numeric. 

```{r change-percent}

chocolate$cocoa_percent<-gsub("%$","",chocolate$cocoa_percent)
chocolate<-transform(chocolate, cocoa_percent = as.numeric(cocoa_percent))
class(chocolate$cocoa_percent)

```

Based on my own experience, as the cocoa_percentage increases, the chocolate tastes worse -- too bitter. Let's see if this theory holds true with the raw data and in the taste of others. 


```{r plot-ratings-cocoa-percentage}


ggplot(chocolate, aes(y = rating, x=cocoa_percent))+
  geom_jitter()+
  stat_smooth(method="lm")+
  labs(title="Relationship between Cocoa Percentage and Rating", y="Rating", x="Cocoa Percentage")


```

```{r fit-linear-model-cocoa-percentage}

linear_reg() %>%
  set_engine("lm") %>%
  fit(rating ~ cocoa_percent, data = chocolate) %>%
  tidy()

```

Using a linear model, the intercept isn't meaningful because no chocolate bar would have 0% of cocoa. Generally, if we increase cocoa percentage, rating of the chocolate decreases.


Taking a closer look at the scatterplot, it seems a quadratic regression model might fit the data better than a linear regression model. Let's explore that. 


```{r fit-quadratic-model}

#create percent squared variable
chocolate$cocoa_percent2<-chocolate$cocoa_percent^2

#fit quad regression model

quad_model <- lm(rating ~ cocoa_percent + cocoa_percent2, data=chocolate)

#view model

summary(quad_model)



```








































