---
title: "Portfolio 8"
name: "Cat Seitz"
date: "3.21.2023"
data: "Thesis analysis - adult & child data - distractor location rt "
output: 
  html_document: 
    theme: cerulean
---

The goal of this portfolio is to examine part of my thesis data. To recap, my thesis is examining distractor suppression in children and adults. Participants are shown a distractor in a location more frequently than other locations in a visual search array. Based on previous studies, we would expect adults to suppress their attention to the high-probability location, but we were unsure when in development children develop this ability. 



```{r load-packages, message=FALSE}
library(tidyverse) 
library(tidyr)
library(rstatix)
library(data.table)
library(afex)
library(emmeans)
library(psych)
library(ggprism)
library(patchwork)
library(magrittr)
library(cowplot)
```

I put all the messy loading in of different data sets and adding in important columns to an R script instead of having it here. 
```{r, include=FALSE}

source("load_data.R", local = knitr::knit_global())

```

### Trim the Data

```{r find-means}

aggregate(rt ~ acc, data = adults, FUN = mean)
aggregate(rt ~ acc, data = adults, FUN = sd)
aggregate(rt ~ acc, data = kids12, FUN = mean)
aggregate(rt ~ acc, data = kids12, FUN = sd)
aggregate(rt ~ acc, data = kids6, FUN = mean)
aggregate(rt ~ acc, data = kids6, FUN = sd)

```

Define trimming criteria according to Van Selst and Jolicoeur 1994.
```{r set_stds_depending_on_set_size}
xsize <- c(4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 20, 
             25, 30, 35, 50, 100)
stds <- c(1.458, 1.68, 1.841, 1.961, 2.05, 2.12, 2.173, 
            2.22, 2.246, 2.274, 2.31, 2.326, 2.391, 2.41, 2.4305, 
            2.45, 2.48, 2.5)
```

Trim the data and compute the percent trimmed
```{r trimming-adults}
trimmedA <- adults[adults$acc==1, ] %>% group_by(id, relative_hp_dist) %>%
           mutate(sdc = ifelse(length(rt)>=100,2.5,approx(xsize,stds,xout=length(rt))$y), avg = mean(rt), stdev = sd(rt)) %>%
           filter(rt <= sdc*stdev+avg & rt >=avg-(sdc*stdev) & rt >=200 & rt<=2500) %>% #exact upper limit =2464.175
           select(id, age, relative_hp_dist, rt, block_num) %>%  #keep these columns in the new data frame
           as.data.frame()


statPrep <- trimmedA %>% group_by(id, relative_hp_dist) %>% summarise(measurement=mean(rt)) %>% as.data.frame()
100-(nrow(trimmedA)/nrow(adults[adults$acc==1, ]))*100
```
5.10% of trials were trimmed from the adult data set. 

```{r trimming-child12}
trimmedC12 <- kids12[kids12$acc==1, ] %>% group_by(id, relative_hp_dist) %>%
           mutate(sdc = ifelse(length(rt)>=100,2.5,approx(xsize,stds,xout=length(rt))$y), avg = mean(rt), stdev = sd(rt)) %>%
           filter(rt <= sdc*stdev+avg & rt >=avg-(sdc*stdev) & rt >=200 & rt<=7590) %>%  #exact upper limit =7586.794
           select(id, age1, relative_hp_dist, rt, block_num1) %>%  #keep these columns in the new data frame
           as.data.frame()


statPrep <- trimmedC12 %>% group_by(id, relative_hp_dist) %>% summarise(measurement=mean(rt)) %>% as.data.frame()
100-(nrow(trimmedC12)/nrow(kids12[kids12$acc==1, ]))*100
```
4.64% of trials were trimmed from the older child data set. 

```{r trimming-child6}
trimmedC6 <- kids6[kids6$acc==1, ] %>% group_by(id, relative_hp_dist) %>%
           mutate(sdc = ifelse(length(rt)>=100,2.5,approx(xsize,stds,xout=length(rt))$y), avg = mean(rt), stdev = sd(rt)) %>%
           filter(rt <= sdc*stdev+avg & rt >=avg-(sdc*stdev) & rt >=200 & rt<=18950) %>% #exact upper limit =18929.79
           select(id, age2, relative_hp_dist, rt, block_num2) %>%  #keep these columns in the new data frame
           as.data.frame()


statPrep <- trimmedC6 %>% group_by(id, relative_hp_dist) %>% summarise(measurement=mean(rt)) %>% as.data.frame()
100-(nrow(trimmedC6)/nrow(kids6[kids6$acc==1, ]))*100
```
6.07% of trials were trimmed from the younger child data set.


### Response Time ANOVA for 3 conditions and 2 ages

```{r change-column-names}

trimmedC12<- trimmedC12 %>%
  rename(
    block_num=block_num1,
    age=age1
  )

trimmedC6<- trimmedC6 %>%
  rename(
    block_num=block_num2,
    age=age2
  )


```


 
```{r combine-columns}

all_data <- rbind(trimmedA, trimmedC12)
 
```

Create a new data frame with the average RT for each relative distractor location per participant, so we can do a repeated measures ANOVA -- eventually -- maybe. 

```{r sum-stat-all}

space <- all_data %>%
  group_by(age, id, relative_hp_dist) %>%
  summarize(rts = mean(rt)
            )
space
  
```

Run ANOVA on 3 conditions first, and if significant, then run in on 5 conditions?

Need to reformat the above df to have a column for each relative_hp_dist/ID so we can average across low-probability locations. 

```{r reformat-all}

space_anova <- setDT(space)
space_anova <- dcast(space_anova,id+age~relative_hp_dist,value.var='rts')

```

```{r avg-lp-all}

space_anova <- space_anova %>%
  mutate(low_prob = (lp_1+lp_2+lp_3)/3)

```

Now, I want to create a smaller graph with just 3 bars: one for the high-probability rts, average of low-probability rts, and no distractor. 

```{r get_info_for_smaller_figure}

df_mod <- subset(space_anova, select=c(id, age, high_prob, absent, low_prob))

df_mod <- reshape2::melt(df_mod, id.var=c('id', 'age'), variable.name= "relative_hp_dist")

```

```{r set-up-data-for-plot}

sum_stats <- df_mod%>%
  group_by(age, relative_hp_dist)%>%
  summarize(mean_rts=mean(value),
            sd_rt=sd(value),
            n_rt=n(),
            se=sd_rt/sqrt(n_rt),
            upper_limit=mean_rts+se,
            lower_limit=mean_rts-se
  )
sum_stats

```

```{r order-bars}
sum_stats$relative_hp_dist <- factor(sum_stats$relative_hp_dist,              # Change ordering manually
                  levels = c("high_prob", "low_prob", "absent"))

```

Plot data. 

```{r plot-first, fig.height=11, fig.width=24}

supp.labs <- c("Adults", "Children")
names(supp.labs) <- c("adult", "child")

a<-ggplot(subset(sum_stats, age %in% c("adult")),aes(x = relative_hp_dist, y = mean_rts, fill=relative_hp_dist)) +
  geom_bar(stat = "identity", show.legend = FALSE)+
  geom_errorbar(aes(ymin=lower_limit, ymax=upper_limit), width=0.2)+
  coord_cartesian(ylim = c(800, 1200))+ 
  #facet_grid(~age, scales="free", labeller = labeller(age=supp.labs)) +
  theme_classic()+
  theme(axis.text=element_text(size=30),
        axis.title=element_text(size=40,face="bold"),
        title = element_text(size = 45)) +
  labs(x = "Distractor Location", y = "Response Time (ms)")+
  labs(title= "Singleton Distractor Present",subtitle = "Adults", tag = "A")+
  scale_fill_manual(values=c('#1b9e77', '#d95f02', '#66a61e')) +
  scale_x_discrete(labels= c("high_prob"="HP loc","low_prob"="LP loc","absent"="Absent"))

b<-ggplot(subset(sum_stats, age %in% c("child")),aes(x = relative_hp_dist, y = mean_rts, fill=relative_hp_dist)) +
  geom_bar(stat = "identity", show.legend = FALSE)+
  geom_errorbar(aes(ymin=lower_limit, ymax=upper_limit), width=0.2)+
  coord_cartesian(ylim = c(1200, 2500))+ 
  #facet_grid(~age, scales="free", labeller = labeller(age=supp.labs)) +
  theme_classic()+
  theme(axis.text=element_text(size=30),
        axis.title=element_text(size=40,face="bold"),
        title = element_text(size = 45)) +
  labs(x = "Distractor Location", y = "Response Time (ms)")+
  labs(title = "  ", subtitle = "Children", tag = " ")+
  scale_fill_manual(values=c('#1b9e77', '#d95f02', '#66a61e')) +
  scale_x_discrete(labels= c("high_prob"="HP loc","low_prob"="LP loc","absent"="Absent"))

plot_grid(a, b, align=c("hv"), label_size=40) 
  


```


Run a 3x2 mixed design ANOVA with distractor location and age as independent variables and rt as the dependent variable. 

```{r ANOVA-all}

model3 <- aov_car(value ~ age*relative_hp_dist + Error(id/relative_hp_dist), data=df_mod)

model3

```

The effect of age was significant F(1,31)=8, p=.008.The effect of distractor location was significant, F(2, 62)= 25.2, p<.001. The interaction was significant, F(2,62)=4.28, p=.025.



### Separate ANOVA for just adults

```{r sum-stats-adults}

spaceA <- trimmedA %>%
  group_by(id, relative_hp_dist) %>%
  summarize(rts = mean(rt)
            )
  
```

Run ANOVA on 3 conditions first, and if significant, then run in on 5 conditions?

Need to reformat the above df to have a column for each relative_hp_dist/ID so we can average across low-probability locations. 

```{r reformat-adults}

space_anovaA <- setDT(spaceA)
space_anovaA <- dcast(space_anovaA,id~relative_hp_dist,value.var='rts')

```

```{r avg-lp-adults}

space_anovaA <- space_anovaA %>%
  mutate(low_prob = (lp_1+lp_2+lp_3)/3)

```

Now, I want to create a smaller graph with just 3 bars: one for the high-probability rts, average of low-probability rts, and no distractor. 

```{r reshape-adults}

df_modA <- subset(space_anovaA, select=c(id, high_prob, absent, low_prob))

df_modA <- reshape2::melt(df_modA, id.var=c('id'), variable.name= "relative_hp_dist")

```

```{r ANOVA-3adults}

modelA <- aov_car(value ~ relative_hp_dist + Error(id/relative_hp_dist), data=df_modA)

modelA

```

There is a difference in rt when presenting the distractor in different locations, F(2,52)=57.25, p<.001. 


The repeated measures ANOVA on just the adults was significant. 

```{r last_anova_test-adults}

model_dist_rtsA <- aov_car(rts ~ relative_hp_dist + Error(id/relative_hp_dist), data=spaceA)

model_dist_rtsA


```

Run t-test to determine significant differences between conditions. 

```{r BC-adults}

df_modA %>%
  pairwise_t_test(
    value ~ relative_hp_dist, paired = TRUE,
    p.adjust.method = "bonferroni"
    )


```

```{r t-test-adults}

space_anovaA %>%
  t.test(x=space_anovaA$low_prob, y=space_anovaA$high_prob, alternative="greater", mu=0,paired = TRUE, conf.level = .95) 
space_anovaA%>%
  t.test(x=space_anovaA$high_prob, y=space_anovaA$absent, alternative="greater", mu=0, paired =TRUE, conf.level = .95) 
space_anovaA%>%
  t.test(x=space_anovaA$low_prob, y=space_anovaA$absent, alternative="greater", mu=0, paired =TRUE, conf.level = .95)

```

### Separate ANOVA for just kids


```{r sum-stat-kids}

spaceK <- trimmedC12 %>%
  group_by(id,relative_hp_dist) %>%
  summarize(rts = mean(rt)
            )

```

Run ANOVA on 3 conditions first, and if significant, then run in on 5 conditions?

Need to reformat the above df to have a column for each relative_hp_dist/ID so we can average across low-probability locations. 

```{r reformat-kids}

space_anovaK <- setDT(spaceK)
space_anovaK <- dcast(space_anovaK,id~relative_hp_dist,value.var='rts')

```

```{r avg-lp-kids}

space_anovaK <- space_anovaK %>%
  mutate(low_prob = (lp_1+lp_2+lp_3)/3)

```

Now, I want to create a smaller graph with just 3 bars: one for the high-probability rts, average of low-probability rts, and no distractor. 

```{r reshape-kids}

df_modK <- subset(space_anovaK, select=c(id,high_prob, absent, low_prob))

df_modK <- reshape2::melt(df_modK, id.var=c('id'), variable.name= "relative_hp_dist")

```

```{r ANOVA-3kids}

modelK <- aov_car(value ~ relative_hp_dist + Error(id/relative_hp_dist), data=df_modK)

modelK

```

The repeated measures ANOVA on just the kids was also significant.

```{r last_anova_test-5kids}

model_dist_rtsK <- aov_car(rts ~ relative_hp_dist + Error(id/relative_hp_dist), data=spaceK)

model_dist_rtsK


```

Run t-test to determine significant differences between conditions. 


```{r t-test-kids}

space_anovaK %>%
  t.test(x=space_anovaK$low_prob, y=space_anovaK$high_prob, alternative="greater", mu=0,paired = TRUE, conf.level = .95) 
space_anovaK%>%
  t.test(x=space_anovaK$high_prob, y=space_anovaK$absent, alternative="greater", mu=0, paired =TRUE, conf.level = .95) 
space_anovaK%>%
  t.test(x=space_anovaK$low_prob, y=space_anovaK$absent, alternative="greater", mu=0, paired =TRUE, conf.level = .95)

```

```{r plot-2}
ggplot(all_data, aes(relative_hp_dist, rt, fill=relative_hp_dist)) +
  geom_bar(stat="summary", fun.y="mean", position="dodge") + 
  facet_grid(.~age) +
  xlab("Distractor Location") + ylab("Response Times (ms)") +
  scale_fill_brewer(palette="Dark2") +
  theme(legend.position="none")

```

### Examine normalized rts

```{r normalized-rts-df}

write.csv(df_mod, "norm_data.csv", row.names=FALSE)

```

```{r import-norm-data}

normrt <- read_csv("norm_data_new.csv", show_col_types = FALSE)
normrt<- subset(normrt, select=c(id...1, age, relative_hp_dist, norm))

```

```{r ANOVA-norm}

model_norm <- aov_car(norm ~ age*relative_hp_dist + Error(id...1/relative_hp_dist), data=normrt)

model_norm

```

```{r reformat-kids-norm}

reform <- setDT(normrt)
reform <- dcast(reform,id...1+age~relative_hp_dist,value.var='norm')

```


```{r t-test-norm}

reform %>%
  t.test(x=reform$low_prob, y=reform$high_prob, alternative="greater", mu=0,paired = TRUE, conf.level = .95) 
reform%>%
  t.test(x=reform$high_prob, y=reform$absent, alternative="greater", mu=0, paired =TRUE, conf.level = .95) 
reform%>%
  t.test(x=reform$low_prob, y=reform$absent, alternative="greater", mu=0, paired =TRUE, conf.level = .95)

```


Set up normalized data plot. 
```{r set-up-data-for-norm-plot}

sum_stats_norm <- normrt%>%
  group_by(relative_hp_dist)%>%
  summarize(mean_rts=mean(norm),
            sd_rt=sd(norm),
            n_rt=n(),
            se=sd_rt/sqrt(n_rt),
            upper_limit=mean_rts+se,
            lower_limit=mean_rts-se
  )
sum_stats_norm

```

```{r order-bars-norm}
sum_stats_norm$relative_hp_dist <- factor(sum_stats_norm$relative_hp_dist,              # Change ordering manually
                  levels = c("high_prob", "low_prob", "absent"))

```

Plot data. 

```{r plot-first-norm, fig.height=11, fig.width=22}

a<-ggplot(data = sum_stats_norm, aes(x = relative_hp_dist, y = mean_rts, fill=relative_hp_dist)) +
  geom_bar(stat = "identity", show.legend = FALSE)+
  geom_errorbar(aes(ymin=lower_limit, ymax=upper_limit), width=0.2)+
  coord_cartesian(ylim = c(.85,1.1))+ 
  theme_classic()+
  theme(axis.text=element_text(size=30),
        axis.title=element_text(size=40,face="bold"),
        title = element_text(size = 40),
        strip.text.x = element_text(size=30)) +
  labs(x = "Distractor Location", y = "Normalized Response Time (%)")+
  labs(title = "Singleton Distractor Present")+
  scale_fill_manual(values=c('#1b9e77', '#d95f02', '#66a61e')) +
  scale_x_discrete(labels= c("high_prob"="HP loc","low_prob"="LP loc","absent"="Absent"))

plot_grid(a,labels = c('A'), label_size=40)
  


```


### Examine block-by-block learning of distractor location

The goal of this section is to examine individual blocks of trials for learning. I'll be taking the difference between response times when the distractor is presented in the low probability locations and response times when the distractor is presented in the high probability location in each block to see roughly how quickly individuals are learning the regularity.


```{r create_new_df_to_transform}
space_block <- all_data %>%
  group_by(id, age, block_num, relative_hp_dist) %>%
  summarize(rts = mean(rt),
            )
space_block
```

```{r transform_df}

space_block <- setDT(space_block)
space_block <- dcast(space_block,id+age+block_num~relative_hp_dist,value.var='rts')

```

Below, I added the average rt for the low probability locations and the difference between the low probability and high probability locations ignoring n/a values. 

```{r add_avg_col}

space_block <- space_block %>%
  mutate(low_prob = rowMeans(select(space_block, c(lp_1,lp_2,lp_3)),na.rm=TRUE)) %>%
  mutate(difference = (low_prob-high_prob))


```


```{r line_plot}
ggplot(data = space_block,aes(x=block_num, y=difference, group=id))+
  geom_line(aes(color=age))+
  labs(title = "Difference in Response Times", subtitle = "for distractor presentation at the low-probability locations and high-probability location by block")+
  theme_classic()+
  labs(x = "Block Number", y = "Difference in RT (ms)")

```


Positive differences indicate that participants were faster when the distractor was presented in the high probability location compared to when it was presented in the low probability locations. The average across all participants is plotted below. These results indicate that the individuals are learning within the first block where the distractor is likely to appear. 

```{r create_df_to_transform}
space2 <- space_block %>%
  group_by(age, block_num) %>%
  summarize(rts = mean(difference, na.rm = TRUE),
            sd_rt=sd(difference, na.rm = TRUE),
            n_rt=n(),
            se=sd_rt/sqrt(n_rt),
            upper_limit=rts+se,
            lower_limit=rts-se
            )
space2

```

```{r line_plot_avg, fig.height=11, fig.width=22}
z<-ggplot(data = space2,aes(x=block_num, y=rts))+
  geom_line(aes(color=age, linewidth=1))+
  geom_point()+
  geom_errorbar(aes(ymin=lower_limit, ymax=upper_limit), width=0.2)+
  labs(title = "Raw RTs")+
  xlab("Block number")+
  ylab(expression(atop("Suppression effect (ms)", paste("(high prob. - low prob.)"))))+
  theme(axis.text=element_text(size=30),
        axis.title=element_text(size=40,face="bold"),
        title = element_text(size = 45),
        legend.text=element_text(size = 30))+
  guides(linewidth="none")


```


```{r anova_test_by_block}

model4 <- aov_car(difference ~ age*block_num + Error(id/block_num), data=space_block)

model4

```

Maybe will need to separate out by age and see if suppression effect by block is significant.

```{r block-adult-anova}

block_adult <- space_block %>%
  filter(age=="adult")

model5 <- aov_car(difference ~ block_num + Error(id/block_num), data=block_adult)

model5

```

```{r block-child-anova}

block_child <- space_block %>%
  filter(age=="child")

model6 <- aov_car(difference ~ block_num + Error(id/block_num), data=block_child)

model6

```

Not sure the below is important -- need to update if what to use

```{r normalized-block-df}

write.csv(space_block, "space_block.csv", row.names=FALSE)

```

```{r import-norm-data-block}

normy <- read_csv("space_block_norm.csv", show_col_types = FALSE)
normy<- subset(normy, select=c(id, age, block_num, diff_norm))

```


```{r anova_test_by_block_norm}

aov_car(diff_norm ~ age*block_num + Error(id/block_num), data=normy)


```
```{r block-adult-anova_norm}

aov_car(diff_norm ~ block_num + Error(id/block_num), data=normy)

```
```{r anova_distractor_rts}

model = aov(diff_norm~factor(block_num)+
                Error(factor(id)), data=normy)
summary(model)

```

```{r line_plot-norm-block}
ggplot(data = normy,aes(x=block_num, y=diff_norm, group=id))+
  geom_line(aes(color=age))+
  labs(title = "Difference in Response Times", subtitle = "for distractor presentation at the low-probability locations and high-probability location by block")+
  theme_classic()+
  labs(x = "Block Number", y = "Difference in RT (ms)")

```

```{r create_df_to_transform-norm}
space_norm <- normy %>%
  group_by(age, block_num) %>%
  summarize(rts = mean(diff_norm, na.rm = TRUE),
            sd_rt=sd(diff_norm, na.rm = TRUE),
            n_rt=n(),
            se=sd_rt/sqrt(n_rt),
            upper_limit=rts+se,
            lower_limit=rts-se
            )
space_norm

```

```{r line_plot_avg-norm, fig.height=18, fig.width=22}
y<-ggplot(data = space_norm,aes(x=block_num, y=rts))+
  geom_line(aes(color=age, linewidth=1))+
  geom_point()+
  geom_errorbar(aes(ymin=lower_limit, ymax=upper_limit), width=0.2)+
  labs(title="Normalized RTs")+
  xlab("Block number")+
  ylab(expression(atop("Suppression effect (%)", paste("(high prob. - low prob.)"))))+
  theme(axis.text=element_text(size=30),
        axis.title=element_text(size=40,face="bold"),
        title = element_text(size = 45),
        legend.text=element_text(size = 30))+
  guides(linewidth="none")

plot_grid(z,y,labels = c('A', 'B'), label_size=40, ncol=1)


```





### Correlation of suppression effect and visual working memory capacity

```{r suppression-effect}

supp <- space_block %>%
  group_by(id)%>%
  summarize(effect = mean(difference, na.rm = TRUE))

supp

```

### Younger children Analyses

Now, let's examine the partial data from children ages 6-7 years old. 

```{r create_new_df_to_transform-kids6}
space_block6 <- trimmedC6 %>%
  group_by(id, block_num, relative_hp_dist) %>%
  summarize(rts = mean(rt),
            )

```

```{r transform_df-kids6}

space_block6 <- setDT(space_block6)
space_block6 <- dcast(space_block6,id+block_num~relative_hp_dist,value.var='rts')

```

```{r add_avg_col-kids6}

space_block6 <- space_block6 %>%
  mutate(low_prob = rowMeans(select(space_block6, c(lp_1,lp_2,lp_3)),na.rm=TRUE)) %>%
  mutate(difference = (low_prob-high_prob))


```


```{r line_plot-kids6}
ggplot(data = space_block6,aes(x=block_num, y=difference, group=id))+
  geom_line()+
  labs(title = "Difference in Response Times", subtitle = "for distractor presentation at the low-probability locations and high-probability location by block")+
  theme_classic()+
  labs(x = "Block Number", y = "Difference in RT (ms)")

```


```{r sum-stat-allC}

spaceC <- kids6 %>%
  filter(acc==1)%>%
  group_by(id, relative_hp_dist) %>%
  summarize(rts = mean(rt)
            )
  
```

Run ANOVA on 3 conditions first, and if significant, then run in on 5 conditions?

Need to reformat the above df to have a column for each relative_hp_dist/ID so we can average across low-probability locations. 

```{r reformat-allC}

space_anovaC <- setDT(spaceC)
space_anovaC <- dcast(space_anovaC,id~relative_hp_dist,value.var='rts')

```

```{r avg-lp-allC}

space_anovaC <- space_anovaC %>%
  mutate(low_prob = (lp_1+lp_2+lp_3)/3)

```

Now, I want to create a smaller graph with just 3 bars: one for the high-probability rts, average of low-probability rts, and no distractor. 

```{r get_info_for_smaller_figureC}

df_modC <- subset(space_anovaC, select=c(id, high_prob, absent, low_prob))

df_modC <- reshape2::melt(df_modC, id.var=c('id'), variable.name= "relative_hp_dist")

```

```{r set-up-data-for-plotC}

sum_statsC <- df_modC%>%
  group_by(relative_hp_dist)%>%
  summarize(mean_rts=mean(value),
            sd_rt=sd(value),
            n_rt=n(),
            se=sd_rt/sqrt(n_rt),
            upper_limit=mean_rts+se,
            lower_limit=mean_rts-se
  )
sum_statsC

```


```{r plot-6}

ggplot(sum_statsC,aes(x = relative_hp_dist, y = mean_rts, fill=relative_hp_dist)) +
  geom_bar(stat = "identity", show.legend = FALSE)+
  geom_errorbar(aes(ymin=lower_limit, ymax=upper_limit), width=0.2)+
  #coord_cartesian(ylim = c(800, 1200))+ 
  #facet_grid(~age, scales="free", labeller = labeller(age=supp.labs)) +
  theme_classic()+
  #theme(axis.text=element_text(size=30),
        #axis.title=element_text(size=40,face="bold"),
        #title = element_text(size = 45)) +
  labs(x = "Distractor Location", y = "Response Time (ms)")+
  labs(title= "Singleton Distractor Present",subtitle = "Kids aged 6-7", tag = "A")+
  scale_fill_manual(values=c('#1b9e77', '#d95f02', '#66a61e')) +
  scale_x_discrete(labels= c("high_prob"="HP loc","low_prob"="LP loc","absent"="Absent"))



```

