---
title: "Portfolio 8"
name: "Cat Seitz"
date: "3.21.2023"
data: "Thesis analysis - adult data - distractor location rt and accuracy"
output: 
  html_document: 
    theme: cerulean
---

```{r load-packages, message=FALSE}
library(tidyverse) 
library(tidyr)
library(rstatix)
library(data.table)
library(afex)
library(emmeans)
library(psych)
library(ggprism)
library(patchwork)
library(magrittr)
library(cowplot)
```


```{r import data}

adults <- read_csv("adult_data.csv", show_col_types = FALSE)
  
```

```{r add-block-and-relative-dist&target-loc}

block_num <- rep(c(1,2,3,4,5,6), each=60, times=28)
adults <- cbind(adults, block_num)



##need to add something for distractor absent trials - I think I added this
adults <- adults %>%
  mutate(relative_hp_dist=
           case_when(dist_loc==0 ~ 4,
                     dist_loc==1 & hp_loc==1 ~ 0,
                     dist_loc==1 & hp_loc==2 ~ 1,
                     dist_loc==1 & hp_loc==3 ~ 2,
                     dist_loc==1 & hp_loc==4 ~ 3,
                     dist_loc==1 & hp_loc==5 ~ 2,
                     dist_loc==1 & hp_loc==6 ~ 1,
                     dist_loc==2 & hp_loc==1 ~ 1,
                     dist_loc==2 & hp_loc==2 ~ 0,
                     dist_loc==2 & hp_loc==3 ~ 1,
                     dist_loc==2 & hp_loc==4 ~ 2,
                     dist_loc==2 & hp_loc==5 ~ 3,
                     dist_loc==2 & hp_loc==6 ~ 2,
                     dist_loc==3 & hp_loc==1 ~ 2,
                     dist_loc==3 & hp_loc==2 ~ 1,
                     dist_loc==3 & hp_loc==3 ~ 0,
                     dist_loc==3 & hp_loc==4 ~ 1,
                     dist_loc==3 & hp_loc==5 ~ 2,
                     dist_loc==3 & hp_loc==6 ~ 3,
                     dist_loc==4 & hp_loc==1 ~ 3,
                     dist_loc==4 & hp_loc==2 ~ 2,
                     dist_loc==4 & hp_loc==3 ~ 1,
                     dist_loc==4 & hp_loc==4 ~ 0,
                     dist_loc==4 & hp_loc==5 ~ 1,
                     dist_loc==4 & hp_loc==6 ~ 2,
                     dist_loc==5 & hp_loc==1 ~ 2,
                     dist_loc==5 & hp_loc==2 ~ 3,
                     dist_loc==5 & hp_loc==3 ~ 2,
                     dist_loc==5 & hp_loc==4 ~ 1,
                     dist_loc==5 & hp_loc==5 ~ 0,
                     dist_loc==5 & hp_loc==6 ~ 1,
                     dist_loc==6 & hp_loc==1 ~ 1,
                     dist_loc==6 & hp_loc==2 ~ 2,
                     dist_loc==6 & hp_loc==3 ~ 3,
                     dist_loc==6 & hp_loc==4 ~ 2,
                     dist_loc==6 & hp_loc==5 ~ 1,
                     dist_loc==6 & hp_loc==6 ~ 0,
           ))

adults <- adults %>%
  mutate(relative_target=
           case_when(target_loc==1 & hp_loc==1 ~ 0,
                     target_loc==2 & hp_loc==1 ~ 1,
                     target_loc==3 & hp_loc==1 ~ 2,
                     target_loc==4 & hp_loc==1 ~ 3,
                     target_loc==5 & hp_loc==1 ~ 2,
                     target_loc==6 & hp_loc==1 ~ 1,
                     target_loc==1 & hp_loc==2 ~ 1,
                     target_loc==2 & hp_loc==2 ~ 0,
                     target_loc==3 & hp_loc==2 ~ 1,
                     target_loc==4 & hp_loc==2 ~ 2,
                     target_loc==5 & hp_loc==2 ~ 3,
                     target_loc==6 & hp_loc==2 ~ 2,
                     target_loc==1 & hp_loc==3 ~ 2,
                     target_loc==2 & hp_loc==3 ~ 1,
                     target_loc==3 & hp_loc==3 ~ 0,
                     target_loc==4 & hp_loc==3 ~ 1,
                     target_loc==5 & hp_loc==3 ~ 2,
                     target_loc==6 & hp_loc==3 ~ 3,
                     target_loc==1 & hp_loc==4 ~ 3,
                     target_loc==2 & hp_loc==4 ~ 2,
                     target_loc==3 & hp_loc==4 ~ 1,
                     target_loc==4 & hp_loc==4 ~ 0,
                     target_loc==5 & hp_loc==4 ~ 1,
                     target_loc==6 & hp_loc==4 ~ 2,
                     target_loc==1 & hp_loc==5 ~ 2,
                     target_loc==2 & hp_loc==5 ~ 3,
                     target_loc==3 & hp_loc==5 ~ 2,
                     target_loc==4 & hp_loc==5 ~ 1,
                     target_loc==5 & hp_loc==5 ~ 0,
                     target_loc==6 & hp_loc==5 ~ 1,
                     target_loc==1 & hp_loc==6 ~ 1,
                     target_loc==2 & hp_loc==6 ~ 2,
                     target_loc==3 & hp_loc==6 ~ 3,
                     target_loc==4 & hp_loc==6 ~ 2,
                     target_loc==5 & hp_loc==6 ~ 1,
                     target_loc==6 & hp_loc==6 ~ 0,))


adults$relative_target[adults$relative_target == 0] <- "high_prob"
adults$relative_target[adults$relative_target == 1] <- "lp_1"
adults$relative_target[adults$relative_target == 2] <- "lp_2"
adults$relative_target[adults$relative_target == 3] <- "lp_3"

adults$relative_hp_dist[adults$relative_hp_dist == 0] <- "high_prob"
adults$relative_hp_dist[adults$relative_hp_dist == 1] <- "lp_1"
adults$relative_hp_dist[adults$relative_hp_dist == 2] <- "lp_2"
adults$relative_hp_dist[adults$relative_hp_dist == 3] <- "lp_3"
adults$relative_hp_dist[adults$relative_hp_dist == 4] <- "absent"

```


### Trim the Data

Define trimming criteria according to Van Selst and Jolicoeur 1994.
```{r set_stds_depending_on_set_size}
xsize <- c(4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 20, 
             25, 30, 35, 50, 100)
stds <- c(1.458, 1.68, 1.841, 1.961, 2.05, 2.12, 2.173, 
            2.22, 2.246, 2.274, 2.31, 2.326, 2.391, 2.41, 2.4305, 
            2.45, 2.48, 2.5)
```

Trim the data and compute the percent trimmed
```{r trimming}
trimmed <- adults[adults$acc==100, ] %>% group_by(id, relative_hp_dist) %>%
           mutate(sdc = ifelse(length(rt)>=100,2.5,approx(xsize,stds,xout=length(RT))$y), avg = mean(rt), stdev = sd(rt)) %>%
           filter(rt <= sdc*stdev+avg & rt >=avg-(sdc*stdev) & rt >=.200) %>%
           select(id, relative_hp_dist, rt, block_num) %>%  #keep these columns in the new data frame
           as.data.frame()


statPrep <- trimmed %>% group_by(id, relative_hp_dist) %>% summarise(measurement=mean(rt)) %>% as.data.frame()
100-(nrow(trimmed)/nrow(adults[adults$acc==100, ]))*100
```



### Examine response times

Find means of each condition. 

```{r create new df with mean rts}

sum_stats <- trimmed%>%
  group_by(relative_hp_dist)%>%
  summarize(mean_rts=mean(rt),
            sd_rt=sd(rt),
            n_rt=28,
            se=sd_rt/sqrt(n_rt),
            upper_limit=mean_rts+se,
            lower_limit=mean_rts-se
  )
sum_stats

```

Below is a plot of the mean response times depending on the location of the distractor. 

```{r plot-rts}
ggplot(data = sum_stats, aes(x = relative_hp_dist, y = mean_rts)) +
  #geom_point()+
  geom_bar(stat = "identity", fill="blue", color='#000000') + ##9E7E38
  geom_errorbar(aes(ymin=lower_limit, ymax=upper_limit), width=0.2)+
  coord_cartesian(ylim = c(700,1050))+
  theme_classic()+
  labs(x = "Distractor Location", y = "Response Time (ms)")+
  labs(title = "Singleton Distractor Present")
  #labs(caption = "An ANOVA test shows a difference in RT depending on distractor location, F(3.28,65.57)=33.3, p<.001.")+
  #theme(axis.text=element_text(size=30),
       # axis.title=element_text(size=40,face="bold"),
      #  title = element_text(size = 40))+
  #scale_x_discrete(labels= c("no_dist"="no-dist","dist_0"="dist-0","dist_1"="dist-1","dist_2"="dist-2","dist_3"="dist-3"))

```

Run ANOVA on 3 conditions first, and if significant, then run in on 5 conditions?


Create a new data frame with the average RT for each relative distractor location per participant, so we can do a repeated measures ANOVA. 

```{r smaller df for 1 line per condition per participant}

space <- trimmed %>%
  group_by(id, relative_hp_dist) %>%
  summarize(rts = mean(rt)
            )
space
  
```

Run an ANOVA on rts. 

```{r last_anova_test}

model_dist_rts <- aov_car(rts ~ relative_hp_dist + Error(id/relative_hp_dist), data=space)

model_dist_rts


```



