---
title: "Portfolio 9"
name: "Cat Seitz"
date: "3.21.2023"
data: "Thesis analysis - adult & child data - distractor location accuracy"
output: 
  html_document: 
    theme: cerulean
---

The goal of this portfolio is to examine part of my thesis data. To recap, my thesis is examining distractor suppression in children and adults. Participants are shown a distractor in a location more frequently than other locations in a visual search array. Based on previous studies, we would expect adults to suppress their attention to the high-probability location, but we were unsure when in development children develop this ability. 


```{r load-packages, message=FALSE}
library(tidyverse) 
library(tidyr)
library(rstatix)
library(data.table)
library(afex)
library(emmeans)
library(psych)
library(ggprism)
library(patchwork)
library(magrittr)
library(cowplot)
```

I put all the messy loading in of different data sets and adding in important columns to an R script instead of having it here. 
```{r, include=FALSE}

source("load_data.R", local = knitr::knit_global())

```






















































