---
title: "Portfolio 9"
name: "Cat Seitz"
date: "3.21.2023"
data: "Thesis analysis - adult & child data - distractor and target location accuracy"
output: 
  html_document: 
    theme: cerulean
---

The goal of this portfolio is to examine part of my thesis data. To recap, my thesis is examining distractor suppression in children and adults. Participants are shown a distractor in a location more frequently than other locations in a visual search array. Based on previous studies, we would expect adults to suppress their attention to the high-probability location, but we were unsure when in development children develop this ability. 


```{r load-packages, message=FALSE}
library(tidyverse) 
library(tidyr)
library(rstatix)
library(data.table)
library(afex)
library(emmeans)
library(psych)
library(ggprism)
library(patchwork)
library(magrittr)
library(cowplot)
```

I put all the messy loading in of different data sets and adding in important columns to an R script instead of having it here. 
```{r, include=FALSE}

source("load_data.R", local = knitr::knit_global())

```

Change columns to have the same name. 

```{r change-column-names}


kids12<- kids12 %>%
  rename(
    block_num=block_num1,
    age=age1
  )

kids6<- kids6 %>%
  rename(
    block_num=block_num2,
    age=age2
  )

```

 Combine dfs of adults and older children. 
 
```{r combine-columns}

acc_data <- rbind(adults, kids12)
 
```

```{r download}

write.csv(acc_data, "accuracy_data.csv", row.names=FALSE)

```


### Examine Accuracy Effects

Tried to include partial accruacy data from a child but it wasn't working correct and I'm not sure why, so I ended up just getting rid of that child. 

```{r take-out}

#acc_26<- acc_data1%>%
#  subset(id == 26)

#acc_26<-acc_26%>%
#  filter(trial_num<181)

#acc_child<- acc_data1%>%
#  subset(id != 26 & age == "child")

#acc_child<- rbind(acc_child, acc_26)
```

```{r}
#acc_data<-acc_data%>%
  #filter(id!=26)

#acc_data<- rbind(acc_data1, acc_26)

#acc_data<-acc_data%>%
#  mutate(acc=acc*100)

#acc_child<-acc_child%>%
#  mutate(acc=acc*100)

```

IDK why the acc is different when summarizing grouped by age

```{r test-acc}

#acc_child%>%
#  group_by(relative_hp_dist)%>%
#  summarize(acc=mean(acc))

#acc_data%>%
#  group_by(age,relative_hp_dist)%>%
#  summarize(acc=mean(acc))

```

```{r real-acc}

acc_data<-acc_data%>%
  subset(id!=26)

acc_data<-acc_data%>%
  mutate(acc=acc*100)

```

First, examine distractor location effects on accuracy. 

```{r create_accuracy_df}

distacc <- acc_data %>%
  group_by(age,relative_hp_dist) %>%
  summarize(accuracy = mean(acc),
            sd_rt=sd(acc),
            n_rt=n(),
            se=sd_rt/sqrt(n_rt),
            upper_limit=accuracy+se,
            lower_limit=accuracy-se
            )

```

```{r set-up-plot}

space <- acc_data %>%
  group_by(age, id, relative_hp_dist) %>%
  summarize(acc = mean(acc)
            )

space_anova <- setDT(space)
space_anova <- dcast(space_anova,id+age~relative_hp_dist,value.var='acc')

space_anova <- space_anova %>%
  mutate(low_prob = (lp_1+lp_2+lp_3)/3)

df_mod <- subset(space_anova, select=c(id, age, high_prob, absent, low_prob))
df_mod <- reshape2::melt(df_mod, id.var=c('id', 'age'), variable.name= "relative_hp_dist")

```

Set up accuracy data to plot. 

```{r set-up-sum-stats-dist}

sum_stats <- df_mod%>%
  group_by(age, relative_hp_dist)%>%
  summarize(mean_acc=mean(value),
            sd_rt=sd(value),
            n_rt=n(),
            se=sd_rt/sqrt(n_rt),
            upper_limit=mean_acc+se,
            lower_limit=mean_acc-se
  )
sum_stats

```


```{r order-bars}
sum_stats$relative_hp_dist <- factor(sum_stats$relative_hp_dist,              # Change ordering manually
                  levels = c("high_prob", "low_prob", "absent"))

```

```{r plot-first}

supp.labs <- c("Adults", "Children")
names(supp.labs) <- c("adult", "child")

a<-ggplot(data = sum_stats, aes(x = relative_hp_dist, y = mean_acc, fill=relative_hp_dist)) +
  geom_bar(stat = "identity", show.legend = FALSE)+
  geom_errorbar(aes(ymin=lower_limit, ymax=upper_limit), width=0.2)+
  coord_cartesian(ylim = c(85,100))+ 
  facet_grid(.~age, labeller = labeller(age=supp.labs)) +
  theme_classic()+
  theme(axis.text=element_text(size=30),
        axis.title=element_text(size=40,face="bold"),
        title = element_text(size = 45),
        strip.text.x = element_text(size=30)) +
  labs(x = "Distractor Location", y = "Accuracy (%)")+
  labs(title = "Singleton Distractor Present")+
  scale_fill_brewer(palette="Dark2") +
  scale_x_discrete(labels= c("high_prob"="HP loc","low_prob"="LP loc","absent"="Absent"))

plot_grid(a,labels = c('A'), label_size=40)
  




```

Run the 3x2 ANOVA on accuracy data. 
```{r ANOVA-all}

model3 <- aov_car(value ~ age*relative_hp_dist + Error(id/relative_hp_dist), data=df_mod)

model3

```
Main effect of age is significant -- Main effect of distractor location is significant -- interaction is not significant. 

```{r holm-correction-acc-all}

df_mod %>%
  pairwise_t_test(
    value ~ relative_hp_dist, paired = TRUE,
    p.adjust.method = "holm"
    )


```

Since the interaction was not significant, we'll exclude age and test the distractor location effect on accuracy across the 5 conditions. 

```{r ANOVA-5-merge-age}

model4 <- aov_car(acc ~ relative_hp_dist + Error(id/relative_hp_dist), data=acc_data)

model4

```

Accuracy is different across all locations. 

```{r plot-first5}
ggplot(acc_data, aes(relative_hp_dist, acc, fill=relative_hp_dist)) +
  geom_bar(stat="summary", position="dodge") + 
  #facet_grid(.~age) +
  xlab("Distractor Location") + ylab("Accuracy (%)") +
  scale_fill_brewer(palette="Dark2") +
  theme(legend.position="none")+
  coord_cartesian(ylim = c(85,105))

```





Second, examine target location effects on accuracy. 

```{r set-up-plot-target}

spaceT <- acc_data %>%
  subset(relative_hp_dist="absent")%>%
  group_by(age, id, relative_target) %>%
  summarize(acc = mean(acc)
            )

space_anovaT <- setDT(spaceT)
space_anovaT <- dcast(space_anovaT,id+age~relative_target,value.var='acc')

space_anovaT <- space_anovaT %>%
  mutate(low_prob = (lp_1+lp_2+lp_3)/3)

df_mod_targ <- subset(space_anovaT, select=c(id, age, high_prob, low_prob))
df_mod_targ <- reshape2::melt(df_mod_targ, id.var=c('id', 'age'), variable.name= "relative_target")

```
```{r set-up-data-for-plot}

sum_statsT <- df_mod_targ%>%
  group_by(age, relative_target)%>%
  summarize(mean_acc=mean(value),
            sd_rt=sd(value),
            n_rt=n(),
            se=sd_rt/sqrt(n_rt),
            upper_limit=mean_acc+se,
            lower_limit=mean_acc-se
  )
sum_statsT

```

```{r plot-first-target, fig.height=22, fig.width=22}

b<-ggplot(data = sum_statsT, aes(x = relative_target, y = mean_acc, fill=relative_target)) +
  geom_bar(stat = "identity", show.legend = FALSE)+
  geom_errorbar(aes(ymin=lower_limit, ymax=upper_limit), width=0.2)+
  coord_cartesian(ylim = c(85,100))+ 
  facet_grid(.~age, labeller = labeller(age=supp.labs)) +
  theme_classic()+
  theme(axis.text=element_text(size=30),
        axis.title=element_text(size=40,face="bold"),
        title = element_text(size = 45),
        strip.text.x = element_text(size=30)) +
  labs(x = "Target Location", y = "Accuracy (%)")+
  labs(title = "Singleton Distractor Absent")+
  scale_fill_brewer(palette="Dark2") +
  scale_x_discrete(labels= c("high_prob"="HP loc","low_prob"="LP loc"))


plot_grid(a, b,labels = c('A','B'), label_size=40, ncol=1)

```

Run the 3x2 ANOVA on accuracy data. 
```{r ANOVA-all-target}

model3 <- aov_car(value ~ age*relative_target + Error(id/relative_target), data=df_mod_targ)

model3

```

For target location accuracy, there is only a main effect of age. 





