---
title: "Portfolio 10"
name: "Cat Seitz"
date: "3.21.2023"
data: "Thesis analysis - adult & child data - target location response times"
output: 
  html_document: 
    theme: cerulean
---

The goal of this portfolio is to examine part of my thesis data. To recap, my thesis is examining distractor suppression in children and adults. Participants are shown a distractor in a location more frequently than other locations in a visual search array. Based on previous studies, we would expect adults to suppress their attention to the high-probability location, but we were unsure when in development children develop this ability. 


```{r load-packages, message=FALSE}
library(tidyverse) 
library(tidyr)
library(rstatix)
library(data.table)
library(afex)
library(emmeans)
library(psych)
library(ggprism)
library(patchwork)
library(magrittr)
library(cowplot)
```

I put all the messy loading in of different data sets and adding in important columns to an R script instead of having it here. 
```{r, include=FALSE}

source("load_data.R", local = knitr::knit_global())

```


### Trim the Data


Define trimming criteria according to Van Selst and Jolicoeur 1994.
```{r set_stds_depending_on_set_size}
xsize <- c(4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 20, 
             25, 30, 35, 50, 100)
stds <- c(1.458, 1.68, 1.841, 1.961, 2.05, 2.12, 2.173, 
            2.22, 2.246, 2.274, 2.31, 2.326, 2.391, 2.41, 2.4305, 
            2.45, 2.48, 2.5)
```

Trim the data and compute the percent trimmed
```{r trimming-adults}
trimmedA <- adults[adults$acc==1, ] %>% group_by(id, relative_hp_dist) %>%
           mutate(sdc = ifelse(length(rt)>=100,2.5,approx(xsize,stds,xout=length(rt))$y), avg = mean(rt), stdev = sd(rt)) %>%
           filter(rt <= sdc*stdev+avg & rt >=avg-(sdc*stdev) & rt >=200 & rt<=2500) %>% #exact upper limit =2464.175
           select(id, age, relative_hp_dist, rt, block_num) %>%  #keep these columns in the new data frame
           as.data.frame()


statPrep <- trimmedA %>% group_by(id, relative_hp_dist) %>% summarise(measurement=mean(rt)) %>% as.data.frame()
100-(nrow(trimmedA)/nrow(adults[adults$acc==1, ]))*100
```
5.10% of trials were trimmed from the adult data set. 

```{r trimming-child12}
trimmedC12 <- kids12[kids12$acc==1, ] %>% group_by(id, relative_hp_dist) %>%
           mutate(sdc = ifelse(length(rt)>=100,2.5,approx(xsize,stds,xout=length(rt))$y), avg = mean(rt), stdev = sd(rt)) %>%
           filter(rt <= sdc*stdev+avg & rt >=avg-(sdc*stdev) & rt >=200 & rt<=7590) %>%  #exact upper limit =7586.794
           select(id, age1, relative_hp_dist, rt, block_num1) %>%  #keep these columns in the new data frame
           as.data.frame()


statPrep <- trimmedC12 %>% group_by(id, relative_hp_dist) %>% summarise(measurement=mean(rt)) %>% as.data.frame()
100-(nrow(trimmedC12)/nrow(kids12[kids12$acc==1, ]))*100
```
4.64% of trials were trimmed from the older child data set. 

```{r trimming-child6}
trimmedC6 <- kids6[kids6$acc==1, ] %>% group_by(id, relative_hp_dist) %>%
           mutate(sdc = ifelse(length(rt)>=100,2.5,approx(xsize,stds,xout=length(rt))$y), avg = mean(rt), stdev = sd(rt)) %>%
           filter(rt <= sdc*stdev+avg & rt >=avg-(sdc*stdev) & rt >=200 & rt<=18950) %>% #exact upper limit =18929.79
           select(id, age2, relative_hp_dist, rt, block_num2) %>%  #keep these columns in the new data frame
           as.data.frame()


statPrep <- trimmedC6 %>% group_by(id, relative_hp_dist) %>% summarise(measurement=mean(rt)) %>% as.data.frame()
100-(nrow(trimmedC6)/nrow(kids6[kids6$acc==1, ]))*100
```

